Does at-issueness predict projection? Further investigations of the Gradient Projection Principle

### 2022-10-21 writing/investigating-GPP.tex
changed paper structure
updated section 2
testing rebase
added notes from 10/21 meeting

@@

\section{Analyzing and diagnosing at-issueness}\label{s2}

@@

- Djärv, Kajsa. 2019. Factive and assertive attitude reports. Philadelphia, PA: Uni- versity of Pennsylvania dissertation. https://repository.upenn.edu/edissertations/ 3645.

@@

\section{Experiments 1-3: Methods}\label{s3}

@@

In the projection block, target stimuli consisted of a fact and a polar question that was ut- tered by a named speaker, as shown in Figure 1B. The polar questions were formed by real- izing the 20 clauses as the complements of the 20 clause-embedding predicates in Figure 1C. Participants were told to imagine that they are at a party and that, on walking into the kitchen, they overhear somebody ask somebody else a question. Projection was measured using the ?certain that? diagnostic (Djärv \& Bacovcin, 2017; Lorson, 2018; Mahler, 2020; Tonhauser et al., 2018): participants were asked to rate whether the speaker was certain of the CC, taking into consideration the fact. They gave their responses on a slider marked ?no? at one end (coded as 0) and ?yes? at the other (coded as 1). Greater speaker commitment to the CC should result in higher slider ratings.

@@

\section{Experiments 1-3: Results}\label{s4}

\subsection{Comparing at-issueness}

\subsection{GPP}

Further analyses:

\begin{itemize}
\item look at how many unique participants

>>>>

\tableofcontents

@@

@@

- Dj\"arv, Kajsa. 2019. Factive and assertive attitude reports. Philadelphia, PA: Uni- versity of Pennsylvania dissertation. https://repository.upenn.edu/edissertations/ 3645.

@@

\section{Experiments 1-3: Methods}\label{s2}

hallo

@@

In the projection block, target stimuli consisted of a fact and a polar question that was ut- tered by a named speaker, as shown in Figure 1B. The polar questions were formed by real- izing the 20 clauses as the complements of the 20 clause-embedding predicates in Figure 1C. Participants were told to imagine that they are at a party and that, on walking into the kitchen, they overhear somebody ask somebody else a question. Projection was measured using the ?certain that? diagnostic (Dj\"arv \& Bacovcin, 2017; Lorson, 2018; Mahler, 2020; Tonhauser et al., 2018): participants were asked to rate whether the speaker was certain of the CC, taking into consideration the fact. They gave their responses on a slider marked ?no? at one end (coded as 0) and ?yes? at the other (coded as 1). Greater speaker commitment to the CC should result in higher slider ratings.

@@

\section{Projection}

Compare projectivity ratings across entailment-cancelling operators. 
\begin{itemize}
  \item is there a difference between projectivity across contexts? 
  \item is there a difference between verbs in terms of how much embedding context makes a difference (semi-factive v factive)?
  \item previous point that non-factive (i.e. veridical) predicates can also project can be made here for other embedding operators as well
\end{itemize}

\section{At-issueness}

At-issueness diagnostics (kind of) work for questions:
\begin{itemize}
  \item asking whether diagnostic (exp. 1q)
  \item Q-A diagnostic (exp. 2q)
\end{itemize}

\section{GPP}

Replicating results from \cite{tbd-variability}: Correlation between NAI \& projection for PolQs found for:
\begin{itemize}
  \item asking whether diagnostic (exp. 1q)
  \item Q-A diagnostic (exp. 2q)
\end{itemize}

\noindent Both of these also show some interesting lexical exceptions:
\begin{itemize}
  \item non-veridical predicates
  \item some specific kinds of reportatives
  \item how can we systematically identify exceptions based on data analysis?
  \item are these the same kinds of exceptions as in the glossa paper?
\end{itemize}

\noindent Further analyses:
\begin{itemize}
  \item look at how many unique participants
